Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Muck around with DFA description

The $\state$ variables are then used to impose match race criteria 4 (if last
in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight
$i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye
then flight $i$ is not first).  These criteria are imposed by \eqref{C3}, which
is a deterministic finite automata (DFA) constraint \cite{Pesant04}.  This
constraint also ensures that if a skipper has finished his matches in flight
$i$ (i.e.\ $\END$) then he has finished his matches in flight $i+1$ (and so
on).

The constraints above are shown pictorially in Figure~\ref{skipper5}, and
corresponds to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
is presented as coloured boxes, and below that is the $\timeSlot$ array. The
arrows represent the channeling constraints \eqref{C1}. The
$\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue
for $\FIRST$, red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of
Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
the right of the schedule is schema for the DFA. Coloured arcs represent a
transition from one state to another. The DFA is encoded as a set of transition
objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we
specify the accepting states, which are all states except the start state
(white) and the bye state (pink).

@@

    \begin{scope}[yshift=5.5cm, scale=0.85]
        \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofglawn,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofglawn,uofgpillarbox}] at (0, 0) {
            \nodepart[text width=2em, align=center] {one}   \textsc{L}
            \nodepart[text width=2em, align=center] {two}   \textsc{L}
            \nodepart[text width=2em, align=center] {three} \textsc{M}
            \nodepart[text width=2em, align=center] {four}  \textsc{F}
            \nodepart[text width=2em, align=center] {five}  \textsc{F}
            \nodepart[text width=2em, align=center] {six}   \textsc{L}
            \nodepart[text width=2em, align=center, text=white] {seven} \textsc{E}
        };

>>>>

The $\state$ variables are then used to impose match race criteria 4 (if last
in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight
$i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye
then flight $i$ is not first).  These criteria are imposed by \eqref{C3}, which
is a deterministic finite automata (DFA) constraint \cite{Pesant04}. The
transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
represent a transition from one state to another. The DFA is encoded as a set
of transition objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition
is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In
addition we specify the accepting states, which are all states except the start
state (white) and the bye state (pink).  This constraint also ensures that if a
skipper has finished his matches in flight $i$ (i.e.\ $\END$) then he has
finished his matches in flight $i+1$ (and so on).

Figure~\ref{skipper5} also shows the skipper-oriented variables and constraints
corresponding to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
is presented as coloured boxes, and below that is the $\timeSlot$ array. The
arrows represent the channeling constraints \eqref{C1}. The
$\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue
for $\FIRST$, red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of
Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened.

@@

    \begin{scope}[yshift=5.5cm, scale=0.85]
        \node at (-5, 0) { \textbf{ Skipper 5: } };

        \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofglawn,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofglawn,uofgpillarbox}] at (0, 0) {
            \nodepart[text width=2em, align=center] {one}   \textsc{L}
            \nodepart[text width=2em, align=center] {two}   \textsc{L}
            \nodepart[text width=2em, align=center] {three} \textsc{M}
            \nodepart[text width=2em, align=center] {four}  \textsc{F}
            \nodepart[text width=2em, align=center] {five}  \textsc{F}
            \nodepart[text width=2em, align=center] {six}   \textsc{L}
            \nodepart[text width=2em, align=center, text=white] {seven} \textsc{E}
        };
